---
title: "Visualization"
author: "Xavier"
date: "April 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Install latest reticulate
#library(devtools)
#install_github("rstudio/reticulate")

library(reticulate)
#use_python('D:\\Anaconda\\python.exe')
```
# 1. Load data




```{r, echo=FALSE}
library('ggplot2')# visualization
library('ggthemes')
library('scales')
library('VIM') # Missing value
library('dplyr')# data manipulation

library('mice')#imputation
```
```{R}
data <- read.csv('../data/housing_price.csv', header = TRUE)


```




As we could see from above, there are 39520 rows of data. For YR_RMDL column, there are 16351 missing values, 61 for AYB, 26 for stories and only 1 for KITCHENS

For Kitchens, it is easy to decide. since most of this kind of property only have one kitchener, so we fill it will mode 1

For YR_RMDL we fill with AYB since if it is missing value it is not remodeled
```{r}

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

#data$KITCHENS[is.na(data$KITCHENS)] <- getmode(data$KITCHENS[!is.na(data$KITCHENS)])



med_diff_built_remodel <-floor(median(data$YR_RMDL[!is.na(data$YR_RMDL)&!is.na(data$AYB)]- 
                                data$AYB[!is.na(data$YR_RMDL)&!is.na(data$AYB)] ))


# Fill AYB and YR_RMDL
#data$YR_RMDL[is.na(data$YR_RMDL)&!is.na(data$AYB)] <-data$AYB[is.na(data$YR_RMDL)&!is.na(data$AYB)]


#Missing Both
#missing_both <- is.na(data$YR_RMDL)&is.na(data$AYB)

#data$AYB[missing_both]<-floor(median(data$AYB[!is.na(data$AYB)]))

#data$YR_RMDL[missing_both]<-data$AYB[missing_both]- med_diff_built_remodel


#missing_built_have_remodel <- (!is.na(data$YR_RMDL)&is.na(data$AYB))
#data$AYB[missing_built_have_remodel] <- data$YR_RMDL[missing_built_have_remodel]-med_diff_built_remodel

#data$STORIES[is.na(data$STORIES)]<-floor(median(data$STORIES[!is.na(data$STORIES)]))
```


##Outliers / Extreme value

By eyeball the data, we can see there is several outliers
```{r}
yr_rmdl_20_index <- data$YR_RMDL==20&!is.na(data$YR_RMDL)
data[yr_rmdl_20_index,]
data$YR_RMDL[yr_rmdl_20_index]=data$AYB[yr_rmdl_20_index]+med_diff_built_remodel
data$AC[data$AC ==0] <- getmode(data$AC[data$AC !=0])
```

```{r}
data$STORIES[data$STORIES>=14] <- floor(median(data$STORIES[data$STORIES<14]))
```
The height of buildings in Washington is limited by the Height of Buildings Act.  	Tallest residential building in Washington, D.C. Tallest building completed in the city in the 2000s has 14 floors

```{r}
#write.csv(data,'../data/pre_data.csv')
```

##Encode

```{r}
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
data$AC <- factor(data$AC,level=c('Y','N'), label=c(1,0))
data$GRADE <- as.numeric(factor(data$GRADE,level=c(
'Low Quality', 'Fair Quality', 'Average', 'Above Average', 'Good Quality', 'Very Good', 'Excellent', 'Superior', 'Exceptional-A', 'Exceptional-B', 'Exceptional-C', 'Exceptional-D', ordered= TRUE)))
data$CNDTN <- as.numeric(factor(data$CNDTN,level=c('Poor', 'Fair', 'Average', 'Good', 'Very Good','Excellent', ordered= TRUE)))
```

#data$HEAT <- as.numeric(data$HEAT)
#data$Year <- as.numeric(format(as.Date(data$SALEDATE), "%Y"))
#data$Month <- as.numeric(format(as.Date(data$SALEDATE), "%M"))
#data$Date <- as.numeric(format(as.Date(data$SALEDATE), "%d"))
#data$SALEDATE <- as.numeric(data$SALEDATE)
data$NATIONALGRID <- as.numeric(data$NATIONALGRID)
data$ASSESSMENT_NBHD <- as.numeric(data$ASSESSMENT_NBHD)
#data$STYLE <- as.numeric(data$STYLE)

deal_style <- function(da){
  
  style <- da$STYLE
  fin_unfin <- ifelse(grepl("(Fin)$", style), 1,0)+
               ifelse(grepl("(Fin|Unfin)$", style), 1,0)
  da$Fin <- fin_unfin
  short_style <-  trim(gsub('(Fin|Unfin)$','',style))
  
  da$ShortStyle <- as.numeric(factor(short_style,level=c('Vacant', 'Default', 'Split Foyer', 'Bi-Level','Split Level' ,'1 Story', '1.5 Story', '2 Story', '2.5 Story', '3 Story', '3.5 Story', '4 Story','4.5 Story', ordered= TRUE)))
  
  return (da)
}
#data <- deal_style(data)

  
data$STRUCT <- as.numeric(data$STRUCT)
data$EXTWALL <- as.numeric(data$EXTWALL)
data$INTWALL <- as.numeric(data$INTWALL)
data$ROOF <- as.numeric(data$ROOF)
data$WARD <- as.numeric(data$WARD)
data$QUADRANT <- as.numeric(data$QUADRANT)

#try






library(xgboost)
fold_num=1
train<-data[data$fold!=fold_num,]
train <- subset(train, select=-c(Id,fold, ASSESSMENT_SUBNBHD,FULLADDRESS,LATITUDE,LONGITUDE,CENSUS_BLOCK))
train$PRICE = log(train$PRICE)
dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)

test<-data[data$fold==fold_num,]
test_price <- test$PRICE
test<-subset(test, select=-c(Id,fold, ASSESSMENT_SUBNBHD,FULLADDRESS,LATITUDE,LONGITUDE,CENSUS_BLOCK))


#CENSUS_BLOCK
test_price <- log(test$PRICE)

dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
watchlist <- list(train=dtrain, test=dtest)

bst <- xgb.train(data=dtrain, max.depth=8, eta=0.03, nthread = 4, nrounds=5000, watchlist=watchlist)
predict_price <- predict(bst, dtest)

#bstDMatrix <- xgboost(data = data.matrix(subset(train, select=-c(PRICE))), label = train$PRICE,  max.depth=5,nthread = 4, max_,nround = 400,verbose = 1,eval_metric='rmse' )
#predict_price<-predict(bstDMatrix,data.matrix(test))
RMLSE_Score(test_price,predict_price, FALSE)




```{r}
library(tictoc)
library(xgboost)

xg_at1<- function(fold_num,roundn = 2600){
  tic()
  train<-data[data$fold!=fold_num,]
  #LATITUDE,LONGITUDE
  train <- subset(train, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  train$PRICE = log(train$PRICE)
  dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)
  
  test<-data[data$fold==fold_num,]
  test_price <- test$PRICE
  test<-subset(test, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  
  
  test_price <- log(test$PRICE)
  
  dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
  watchlist <- list(train=dtrain, test=dtest)
  
  bst <- xgb.train(data=dtrain, max.depth=8, eta=0.02, nthread = 4, nrounds=2600, watchlist=watchlist,verbose = 0)
  predict_price <- predict(bst, dtest)
  RMLSE_Score(test_price,predict_price, FALSE)
  toc()
  return (cbind(data[data$fold==fold_num,]$Id,predict_price,test_price))

}


#bstDMatrix <- xgboost(data = data.matrix(subset(train, select=-c(PRICE))), label = train$PRICE,  max.depth=5,nthread = 4, max_,nround = 400,verbose = 1,eval_metric='rmse' )
#predict_price<-predict(bstDMatrix,data.matrix(test))
#RMLSE_Score(test_price,predict_price, FALSE)

at1_1 <-xg_at1(1)

at1_2 <-xg_at1(2)
at1_3 <-xg_at1(3)
at1_4 <-xg_at1(4)
at1_5 <-xg_at1(5)

total<-data.frame(rbind(at1_1,at1_2,at1_3,at1_4,at1_5))
RMLSE_Score(total$test_price,total$predict_price, FALSE)
to_sub <-data.frame(Id=total$V1,PRICE=exp(total$predict_price))
#write.csv(to_sub,'../first.csv',row.names = FALSE)
```

```{r}
#full_name <- trim(data$FULLADDRESS)
#data$StreetName <- (trim(gsub('^\\s*\\d+','', data$FULLADDRESS)))
#data$StreetName[data$StreetName ==''] <- NA
xg_at2<- function(fold_num,roundn = 2600){
  tic()
  
  train<-data[data$fold!=fold_num,]
  train<-train[as.Date(train$SALEDATE)>=as.Date('1990-01-01'),]

  #LATITUDE,LONGITUDE
  train <- subset(train, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  train$PRICE = log(train$PRICE)
  dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)
  
  test<-data[data$fold==fold_num,]
  test_price <- test$PRICE
  test<-subset(test, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  
  
  test_price <- log(test$PRICE)
  
  dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
  watchlist <- list(train=dtrain, test=dtest)
  
  bst <- xgb.train(data=dtrain, max.depth=8, eta=0.02, nthread = 4, nrounds=3000, watchlist=watchlist,verbose = 0)
  predict_price <- predict(bst, dtest)
  RMLSE_Score(test_price,predict_price, FALSE)
  toc()
  return (cbind(data[data$fold==fold_num,]$Id,predict_price,test_price))

}

at2_1 <-xg_at2(1)

at2_2 <-xg_at2(2)
at2_3 <-xg_at2(3)
at2_4 <-xg_at2(4)
at2_5 <-xg_at2(5)

total<-data.frame(rbind(at2_1,at2_2,at2_3,at2_4,at2_5))
RMLSE_Score(total$test_price,total$predict_price, FALSE)
to_sub <-data.frame(Id=total$V1,PRICE=exp(total$predict_price))

```


```{r}

xg_at3<- function(fold_num,roundn = 2600){
  tic()
  
  temp_data <- data
  temp_data$SalevYB <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$AYB
  temp_data$SalevYI <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$EYB

  train<-temp_data[temp_data$fold!=fold_num,]
  train<-train[as.Date(train$SALEDATE)>=as.Date('1990-01-01'),]
  

  train <- subset(train, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  train$PRICE = log(train$PRICE)
  dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)
  
  test<-temp_data[temp_data$fold==fold_num,]
  test_price <- test$PRICE
  test<-subset(test, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  
  
  test_price <- log(test$PRICE)
  
  dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
  watchlist <- list(train=dtrain, test=dtest)
  
  bst <- xgb.train(data=dtrain, max.depth=8, eta=0.02, nthread = 4, nrounds=3000, watchlist=watchlist,verbose = 0)
  predict_price <- predict(bst, dtest)
  RMLSE_Score(test_price,predict_price, FALSE)
  toc()
  return (cbind(data[data$fold==fold_num,]$Id,predict_price,test_price))

}

at3_1 <-xg_at3(1)

at3_2 <-xg_at3(2)
at3_3 <-xg_at3(3)
at3_4 <-xg_at3(4)
at3_5 <-xg_at3(5)

total<-data.frame(rbind(at3_1,at3_2,at3_3,at3_4,at3_5))
RMLSE_Score(total$test_price,total$predict_price, FALSE)
to_sub <-data.frame(Id=total$V1,PRICE=exp(total$predict_price))
#write.csv(to_sub,'../first.csv',row.names = FALSE)

#this is the best
```

```{r}
# ZHE GE CAI SHI
temp_data <- data
temp_data$SalevYB <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$AYB
temp_data$SalevYI <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$EYB
temp_data$HEAT <- as.character(data$HEAT)
temp_data$HEAT[temp_data$HEAT=='Air Exchng'|
                temp_data$HEAT=='Elec Base Brd'|
                 temp_data$HEAT=='Evp Cool'|
                 temp_data$HEAT=='Hot Water Rad'|
                 temp_data$HEAT=='Ind Unit'|
                 temp_data$HEAT=='Wall Furnace'|
                 temp_data$HEAT=='Water Base Brd'|
                 temp_data$HEAT=='Ht Pump'|
                 temp_data$HEAT=='Gravity Furnac'
                 ] <- 1
temp_data$HEAT[temp_data$HEAT=='Air-Oil'|
                temp_data$HEAT=='Electric Rad'|
                 temp_data$HEAT=='Forced Air'|
                temp_data$HEAT=='Warm Cool'
                 ] <- 2
temp_data$HEAT[temp_data$HEAT=='No Data']<-0
temp_data$HEAT<-as.numeric(temp_data$HEAT)
temp_data$SALEDATE <- as.Date(paste(format(as.Date(data$SALEDATE), "%Y-%m"),"-01",sep=""))


xg_at4<- function(fold_num,roundn = 2600){
  tic()
  
  train<-temp_data[temp_data$fold!=fold_num,]
  train$PRICE = log(train$PRICE)
  train<-train[as.Date(train$SALEDATE)>=as.Date('1990-01-01'),]
  #up <- mean(train$PRICE)+3*sd(train$PRICE)
  #low <- mean(train$PRICE)-3*sd(train$PRICE)
  #train <- train[train$PRICE<=up,]
  
  train <- subset(train, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)
  
  test<-temp_data[temp_data$fold==fold_num,]
  test_price <- test$PRICE
  test<-subset(test, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  
  test_price <- log(test$PRICE)
  
  dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
  watchlist <- list(train=dtrain, test=dtest)
  
  bst <- xgb.train(data=dtrain, max.depth=8, eta=0.02, nthread = 4, nrounds=4000, watchlist=watchlist,verbose = 0)
  predict_price <- predict(bst, dtest)
  RMLSE_Score(test_price,predict_price, FALSE)
  toc()
  return (cbind(data[data$fold==fold_num,]$Id,predict_price,test_price))

}

at4_1 <-xg_at4(1)
at4_2 <-xg_at4(2)
at4_3 <-xg_at4(3)
at4_4 <-xg_at4(4)
at4_5 <-xg_at4(5)

total<-data.frame(rbind(at4_1,at4_2,at4_3,at4_4,at4_5))
RMLSE_Score(total$test_price,total$predict_price, FALSE)
to_sub <-data.frame(Id=total$V1,PRICE=exp(total$predict_price))
#write.csv(to_sub,'../first.csv',row.names = FALSE)

```

```{r}
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
full_name <- trim(data$FULLADDRESS)

r <- regexpr("^\\s*\\d+", full_name)
data$Number <- rep(NA,length(full_name))
data$Number[r!=-1] <- trim(regmatches(full_name, r))

#data$Number <- as.numeric(trim(regmatches(full_name,regexpr("^\\s*\\d+",full_name))))
#data$Number <- as.numeric(trim(gsub('\\D+.*','' ,data$FULLADDRESS)))

data$StreetName <- (trim(gsub('^\\s*\\d+','', full_name)))

street_name_short <- trim(gsub('\\s+[E,S,W,N]{1,2}$','',full_name))
street_name_short[street_name_short ==''] <- NA


##data$StreetDirection <- as.numeric(factor(trim(regmatches(data$StreetName,regexpr("\\s+[E,S,W,N]{1,2}$",data$StreetName)))))

r <- regexpr("\\s+[E,S,W,N]{1,2}$", data$StreetName)
data$StreetDirection <- rep(NA,length(data$StreetName))
data$StreetDirection[r!=-1] <- trim(regmatches(data$StreetName, r))

data$Number <-as.numeric(data$Number)
data$StreetNameShort <-as.numeric(factor(street_name_short))
data$StreetDirection <-as.numeric(factor(data$StreetDirection))

data$CENSUS_BLOCK_NUM <- as.numeric(trim(gsub('^\\d+\\s+','', data$CENSUS_BLOCK)))




```
NOTE! THERE IS NA

```{r}
temp_data <- data
temp_data$SalevYB <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$AYB
temp_data$SalevYI <- as.numeric(format(as.Date(data$SALEDATE),'%Y'))-data$EYB
temp_data$HEAT <- as.character(data$HEAT)
temp_data$HEAT[temp_data$HEAT=='Air Exchng'|
                temp_data$HEAT=='Elec Base Brd'|
                 temp_data$HEAT=='Evp Cool'|
                 temp_data$HEAT=='Hot Water Rad'|
                 temp_data$HEAT=='Ind Unit'|
                 temp_data$HEAT=='Wall Furnace'|
                 temp_data$HEAT=='Water Base Brd'|
                 temp_data$HEAT=='Ht Pump'|
                 temp_data$HEAT=='Gravity Furnac'
                 ] <- 1
temp_data$HEAT[temp_data$HEAT=='Air-Oil'|
                temp_data$HEAT=='Electric Rad'|
                 temp_data$HEAT=='Forced Air'|
                temp_data$HEAT=='Warm Cool'
                 ] <- 2
temp_data$HEAT[temp_data$HEAT=='No Data']<-0
temp_data$HEAT<-as.numeric(temp_data$HEAT)
temp_data$SALEDATE <- as.Date(paste(format(as.Date(data$SALEDATE), "%Y-%m"),"-01",sep=""))


xg_at5<- function(fold_num,from_fold,roundn = 2600){
  tic()
  
  train<-temp_data[temp_data$fold==from_fold,]
  train$PRICE = log(train$PRICE)
  train<-train[as.Date(train$SALEDATE)>=as.Date('1990-01-01'),]
  #up <- mean(train$PRICE)+3*sd(train$PRICE)
  #low <- mean(train$PRICE)-3*sd(train$PRICE)
  #train <- train[train$PRICE<=up,]
  
  train <- subset(train, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  dtrain <- xgb.DMatrix(data = data.matrix(subset(train, select=-c(PRICE))), label=train$PRICE)
  
  test<-temp_data[temp_data$fold==fold_num,]
  test_price <- test$PRICE
  test<-subset(test, select=-c(Id,fold,ASSESSMENT_SUBNBHD,FULLADDRESS,NATIONALGRID,CENSUS_BLOCK))
  
  
  test_price <- log(test$PRICE)
  
  dtest <- xgb.DMatrix(data = data.matrix(subset(test, select=-c(PRICE))), label=test_price)
  watchlist <- list(train=dtrain, test=dtest)
  
  bst <- xgb.train(data=dtrain, max.depth=8, eta=0.02, nthread = 4, nrounds=3000, watchlist=watchlist,verbose = 0)
  predict_price <- predict(bst, dtest)
  RMLSE_Score(test_price,predict_price, FALSE)
  toc()
  return (cbind(data[data$fold==fold_num,]$Id,predict_price,test_price))

}

#at4_1 <-xg_at4(1)
#at4_2 <-xg_at4(2)
#at4_3 <-xg_at4(3)
#at4_4 <-xg_at4(4)
at5_5 <-xg_at5(5,4)
at5_5 <-xg_at5(5,3)
at5_5 <-xg_at5(5,2)
at5_5 <-xg_at5(5,1)

total<-data.frame(rbind(at4_1,at4_2,at4_3,at4_4,at4_5))
RMLSE_Score(total$test_price,total$predict_price, FALSE)
to_sub <-data.frame(Id=total$V1,PRICE=exp(total$predict_price))
#write.csv(to_sub,'../first.csv',row.names = FALSE)
```
```{r}
importance <- xgb.importance(model = bst)

```
